Toadflax Analysis

### 2024-03-08 toadflax_report.qmd
final final

ggplotly(scores.type,
         width = 700) %>%
  layout(legend = list(title = "")) %>%
  config(
    displayModeBar = TRUE,
    displaylogo = FALSE,
    modeBarButtonsToRemove = list('lasso2d', 
                                  'hoverClosestCartesian',
                                  'hoverCompareCartesian')
  )
```
```{r save files6, echo = F}
ggsave(filename = "Toadflax PCA - All Type.png",
       plot = scores.type,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

loadings.ggplot +
  geom_text(data = loadings.plot,
            aes(PC1, PC2, label = compound))
```
```{r save files6, echo = F}
ggsave(filename = "Toadflax PCA - Loadings Plot Basic.png",
       plot = loadings.ggplot,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.post.natrem, scores.type, ncol = 2)
```
```{r save files1, echo = F}
ggsave(filename = "Toadflax PCA Scores - Type_All.png",
       plot = scores.type,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
ggsave(filename = "Toadflax PCA (Post) - DT, YT, Synthetic.png",
       plot = scores.type,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.pre.natrm, scores.type, ncol = 2)
```
```{r save files2, echo = F}
ggsave(filename = "Toadflax PCA (Pre) - DT, YT, Synthetic.png",
       plot = scores.pre.natrm,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

```
```{r save files3, echo = F}
ggsave(filename = "Toadflax PCA (Post) - Hybrids.png",
       plot = scores.post.hybrids,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

```
```{r save files4, echo = F}
ggsave(filename = "Toadflax PCA (Post) - Hybrids with entire.png",
       plot = scores.post.hybrids.wold,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.pre.hybrids, scores.type, ncol = 2)
```
```{r save files5, echo = F}
ggsave(filename = "Toadflax PCA (Pre) - Hybrids.png",
       plot = scores.pre.hybrids,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

```
```{r save files6, echo = F}
ggsave(filename = "Toadflax PCA - Type_Plant.png",
       plot = scores.plant,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.post.hbrrad, scores.plant, ncol = 2)
```
```{r save files7, echo = F}
ggsave(filename = "Toadflax PCA (Post_Plant_NBR RAD).png",
       plot = scores.post.hbrrad,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.pre.hbrrad, scores.plant, ncol = 2)
```
```{r save files8, echo = F}
ggsave(filename = "Toadflax PCA (Pre_Plant_NBR RAD).png",
       plot = scores.pre.hbrrad ,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

>>>>

ggplotly(scores.type,
         width = 700) %>%
  layout(legend = list(title = "")) %>%
  config(
    displayModeBar = TRUE,
    displaylogo = FALSE,
    modeBarButtonsToRemove = list('lasso2d', 
                                  'hoverClosestCartesian',
                                  'hoverCompareCartesian')
  )
```
```{r save files1, echo = F}
ggsave(filename = "Toadflax PCA - All Type.png",
       plot = scores.type,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

loadings.ggplot +
  geom_text(data = loadings.plot,
            aes(PC1, PC2, label = compound))
```
```{r save files2, echo = F}
ggsave(filename = "Toadflax PCA - Loadings Plot Basic.png",
       plot = loadings.ggplot,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.post.natrem, scores.type, ncol = 2)
```
```{r save files3, echo = F}
ggsave(filename = "Toadflax PCA Scores - Type_All.png",
       plot = scores.type,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
ggsave(filename = "Toadflax PCA (Post) - DT, YT, Synthetic.png",
       plot = scores.type,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.pre.natrm, scores.type, ncol = 2)
```
```{r save files4, echo = F}
ggsave(filename = "Toadflax PCA (Pre) - DT, YT, Synthetic.png",
       plot = scores.pre.natrm,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

```
```{r save files5, echo = F}
ggsave(filename = "Toadflax PCA (Post) - Hybrids.png",
       plot = scores.post.hybrids,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

```
```{r save files6, echo = F}
ggsave(filename = "Toadflax PCA (Post) - Hybrids with entire.png",
       plot = scores.post.hybrids.wold,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.pre.hybrids, scores.type, ncol = 2)
```
```{r save files7, echo = F}
ggsave(filename = "Toadflax PCA (Pre) - Hybrids.png",
       plot = scores.pre.hybrids,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

```
```{r save files8, echo = F}
ggsave(filename = "Toadflax PCA - Type_Plant.png",
       plot = scores.plant,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.post.hbrrad, scores.plant, ncol = 2)
```
```{r save files9, echo = F}
ggsave(filename = "Toadflax PCA (Post_Plant_NBR RAD).png",
       plot = scores.post.hbrrad,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>

@@

grid.arrange(scores.pre.hbrrad, scores.plant, ncol = 2)
```
```{r save files10, echo = F}
ggsave(filename = "Toadflax PCA (Pre_Plant_NBR RAD).png",
       plot = scores.pre.hbrrad ,
       path = "toadflax_plots/",
       width = 6,
       height = 4)
```
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Buttons</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
  margin: 0 200px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
.button-container {
  display: flex;
  justify-content: center;
  margin-bottom: 10px;
}
</style>
</head>
<body>
